Stateless Model Checking with Data-Race Preemption Points

### 2016-08-13 oopsla-16/evaluation.tex
Update number of frms-for-realsies

{\bf Suppressing ``malloc-recycle'' false positives.}
In \sect{\ref{sec:recycle}} we showed the soundness of suppressing data race reports between two heap accesses when the surrounding memory was re-allocated in between.
In Table~\ref{tab:drstatistix}, the column ``Malloc-recycle DRs'' shows the total number of such data-race candidates for each test program.
In total, 902 data-races fit the malloc-recycle pattern across all tests,
only 69 of which were observed to avoid the re-allocation in an alternate interleaving.
Our proof in \sect{\ref{sec:recycle}} guarantees the safety of pruning all 833 other state spaces.

Among those 69 true data-races, %which initially fit the malloc-recycle pattern,
none exposed a new bug when used as a PP.
This suggests that for other data-race tools,
suppressing malloc-recycle candidates may be a productive heuristic,
even if unsound without Iterative Deepening.
However, \quicksand~was able to correctly identify the 69 violations of that heuristic (among 30 distinct tests),
and fall back to classifying them with DPOR.
%which we consider a much stronger verification.

>>>>

{\bf Suppressing ``malloc-recycle'' false positives.}
In \sect{\ref{sec:recycle}} we showed the soundness of suppressing data race reports between two heap accesses when the surrounding memory was re-allocated in between.
In Table~\ref{tab:drstatistix}, the column ``Malloc-recycle DRs'' shows the total number of such data-race candidates for each test program.
In total, \revisionz{965} data-races fit the malloc-recycle pattern across all tests,
% NB. Calculated this by grepping QS-LHB id-logs for "for realsies" (see quicksand pp.c).
only \revisionz{64} of which were observed to avoid the re-allocation in an alternate interleaving.
Our proof in \sect{\ref{sec:recycle}} guarantees the safety of pruning all \revisionz{901} other state spaces.

Among those \revisionz{64} true data-races, %which initially fit the malloc-recycle pattern,
none exposed a new bug when used as a PP.
This suggests that for other data-race tools,
suppressing malloc-recycle candidates may be a productive heuristic,
even if unsound without Iterative Deepening.
However, \quicksand~was able to correctly identify the \revisionz{64} violations of that heuristic (among \revisionz{26} distinct tests),
and fall back to classifying them with DPOR.
%which we consider a much stronger verification.
